{\bf {\Large Detiding time series of dissolved oxygen for improved estimates of ecosystem metabolism}}

### 2014-09-24 assess.Rnw
changed means to medians

To test the ability of the weighted regression to filter the \ac{DO} signal for apparent tide effects, multiple time series with known characteristics were simulated and filtered.  Observed \ac{DO} time series were simulated as the sum of variation from biological processes and physical effects related to tidal advection:  
\begin{equation} \label{do_obs}
DO_{obs} = DO_{bio} + DO_{adv}
\end{equation}
Biological \ac{DO} signals are inherently noisy \citep{Batt12} and variance can be further described as:
\begin{equation} \label{do_bio} 
DO_{bio} = DO_{die} + DO_{unc}
\end{equation} 
\begin{equation} \label{do_unc}
DO_{unc} = \epsilon_{obs} + \epsilon_{proc}
\end{equation}
where the biological \ac{DO} signal is the sum of diel variation plus uncertainty or noise.  Total uncertainty in the biological \ac{DO} signal is described as variation from observation and process uncertainty \citep{Hilborn97}.  Multiple time series at 30 minute time steps over 30 days were created by varying the relative magnitudes of each of the components of observed \ac{DO} in \cref{do_obs,do_bio,do_unc} to test the effectiveness of weighted regression under different scenarios.  Accordingly, observed \ac{DO} was generalized as the additive combination of four time series (\cref{fig:do_sim}):
\begin{equation} \label{do_obs_all}
DO_{obs} = DO_{adv} + DO_{die} + \epsilon_{obs} + \epsilon_{pro}
\end{equation}

@@

A semidiurnal tidal series was simulated as a sine wave with a period of 12.5 hours to represent the principal lunar component \citep{Foreman89}.  The amplitude was set to 1 meter and centered  at 4 meters.  Initial assessments indicated that tide type (i.e., diurnal, semidiurnal, mixed) did not signifcantly affect the outcome of the results and a semidiurnal time series was used to reduce the total number of simulations.  The tidal time series was added to the biological \ac{DO} series to simulate \ac{DO} changes with advection, $DO_{adv}$ (\cref{do_obs_all,fig:do_sim}). Conceptually, this vector represents the rate of change in \ac{DO} as a function of horizontal water movement from tidal advection such that:
\begin{equation} \label{deltdo}
\frac{\delta DO_{adv}}{\delta t} = \frac{\delta DO}{\delta x} \cdot \frac{\delta x}{\delta t}
\end{equation}
\begin{equation} \label{deltx}
\frac{\delta x}{\delta t} = k \cdot \frac{\delta H}{\delta t}
\end{equation}
where the first derivative of the tidal time series, as change in height over time $\delta H / \delta t$, is multiplied by a constant $k$, to estimate horizontal tidal excursion over time, $\delta x / \delta t$.  The horizontal excursion is assumed to be associated with a horizontal \ac{DO} change, $\delta DO / \delta x$, such that the product of the two estimates the \ac{DO} change at each time step from advection, $DO_{adv}$. In practice, the simulated tidal signal was used to estimate $DO_{adv}$:
\begin{equation} \label{do_advp}
DO_{adv} \propto H
\end{equation}
\begin{equation} \label{do_adv}
DO_{adv} = 2\cdot a + a \cdot \frac{H- \min H}{\max H - \min H}
\end{equation}
where $a$ is analogous to $k$ in \cref{deltx} and is chosen as the transformation parameter to standardize change in \ac{DO} from tidal height change to desired units.  For example, $a = 1$ will convert $H$ to a scale that simulates changes in \ac{DO} from tidal advection that range from +/- 1 mg L$^{-1}$.  The final time series for observed \ac{DO} was the sum of biological \ac{DO} and advection \ac{DO} (\cref{do_obs,fig:do_sim}).

@@

Multiple time series were simulated by varying the conditions in \cref{do_obs,do_bio,do_unc,do_obs_all,do_sin,do_unc_n,deltdo,deltx,do_advp,do_adv}. Specifically, the simulated data varied in the relative amount of noise in the measurement ($e_{pro}$, $e_{obs}$), relative amplitude of the diel \ac{DO} component ($DO_{die}$), and degree of association of the tide with the \ac{DO} signal ($DO_{adv}$).  Three levels were evaluated for each variable: relative noise as 0, 1, and 2 standard deviations for both process and observation uncertainty, amplitude of diel biological \ac{DO} as 0, 1, and 2 mg L$^{-1}$, and \ac{DO} change from tidal advection as 0, 1, and 2 mg L$^{-1}$. A total of 81 time series were created based on the unique combinations of parameters (\cref{fig:sim_ex}).  Three half window widths for each variable (day, hour of day, and tide height) were evaluated for each simulation: decimal time as 1, 3, and 6 days, time of day as 1, 3, and 6 hours, and tidal height as 0.25, 0.5, and 1 as a proportion of the total range given the height at the center of the window.  The window widths were chosen based on preliminary assessments that suggested variation in model performance was adequately captured by these values.  In total, 27 window width combinations were evaluated for each of 81 simulated time series, producing results for 2187 weighted regressions.

The detided or normalized values for each regression were compared to the simulated data to evaluate the ability of weighted regression to reproduce the biological \ac{DO} signals. Results were summarized using Pearson correlation coefficients and the \ac{RMSE} between the detided time series and the biological \ac{DO} time series as a known component of the observed.  Overall, the weighted regressions provided accurate results for the detided time series compared to the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2},   results for each simulation can be viewed using the link in the \hyperref[multi]{multimedia} section).  Mean correlation for all time series and window widths between the detided and biological values was \Sexpr{form_fun(perf_means['cor'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'cor'])} to \Sexpr{form_fun(perf_rngs[2, 'cor'])}.  Mean error was \Sexpr{form_fun(perf_means['err'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'err'], 0, 0, 0)} to \Sexpr{form_fun(perf_rngs[2, 'err'])}.  Simulations with very poor performance (e.g., negative correlations) were those that had minimum widths for day windows and maximum widths for hour windows, or were those with the \ac{DO} signal composed entirely of noise from observation uncertainty. Conversely, simulations with detided time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero) were those for which there was no biological or tidal influence.  Although these examples do not represent real-world scenarios, they were included in the simulations to provide verification that the weighted regression provided reasonable results given extremes.

Characteristics of \ac{DO} time series that contributed to improved model performance were increasing amplitude of the diel \ac{DO} component ($DO_{die}$) and increasing process uncertainty ($e_{pro}$), whereas increasing observation uncertainty contributed to decreased performance (\cref{tab:dtd_perf1,fig:err_surf1}).  Model performance was minimally influenced by magnitude of the tidal advection component ($DO_{adv}$), although performance decreased slightly with increasing tidal effects.  Increasing widths for day and tidal proportion windows contributed to increasing model performance, whereas the opposite was true for increasing hour windows (\cref{tab:dtd_perf2,fig:err_surf2}).  Graphical summaries of model performance by simulation parameters (\cref{fig:err_surf1}) and half window widths (\cref{fig:err_surf2}) support the general trends described by \cref{tab:dtd_perf1,tab:dtd_perf2}.

>>>>

To test the ability of the weighted regression to filter the \ac{DO} signal for apparent tide effects, multiple time series with known characteristics were simulated and filtered.  A simulation approach was used prior to application with real data given that the true biological signal can be created as a known component for comparison with the filtered results from weighted regression. The following describes the theoretical basis for developing the simulated time series.  Observed \ac{DO} time series were simulated as the sum of variation from biological processes and physical effects related to tidal advection:  
\begin{equation} \label{do_obs}
DO_{obs} = DO_{bio} + DO_{adv}
\end{equation}
Biological \ac{DO} signals are inherently noisy \citep{Batt12} and variance can be further described as:
\begin{equation} \label{do_bio} 
DO_{bio} = DO_{die} + DO_{unc}
\end{equation} 
\begin{equation} \label{do_unc}
DO_{unc} = \epsilon_{obs} + \epsilon_{proc}
\end{equation}
where the biological \ac{DO} signal is the sum of diel variation plus uncertainty or noise.  Total uncertainty in the biological \ac{DO} signal is described as variation from observation and process uncertainty \citep{Hilborn97}.  Multiple time series at 30 minute time steps over 30 days were created by varying the relative magnitudes of each of the components of observed \ac{DO} in \cref{do_obs,do_bio,do_unc} to test the effectiveness of weighted regression under different scenarios.  Accordingly, observed \ac{DO} was generalized as the additive combination of four separate time series (\cref{fig:do_sim}):
\begin{equation} \label{do_obs_all}
DO_{obs} = DO_{adv} + DO_{die} + \epsilon_{obs} + \epsilon_{pro}
\end{equation}

@@

A semidiurnal tidal series was simulated with a period of 12.5 hours to represent the principal lunar component \citep{Foreman89}.  The amplitude was set to 1 meter and centered  at 4 meters.  The tidal time series was added to the biological \ac{DO} series to simulate \ac{DO} changes with advection, $DO_{adv}$ (\cref{do_obs_all,fig:do_sim}). Conceptually, this vector represents the rate of change in \ac{DO} as a function of horizontal water movement from tidal advection such that:
\begin{equation} \label{deltdo}
\frac{\delta DO_{adv}}{\delta t} = \frac{\delta DO}{\delta x} \cdot \frac{\delta x}{\delta t}
\end{equation}
\begin{equation} \label{deltx}
\frac{\delta x}{\delta t} = k \cdot \frac{\delta H}{\delta t}
\end{equation}
where the first derivative of the tidal time series, as change in height over time $\delta H / \delta t$, is multiplied by a constant $k$, to estimate horizontal tidal excursion over time, $\delta x / \delta t$.  The horizontal excursion is assumed to be associated with a horizontal \ac{DO} change, $\delta DO / \delta x$, such that the product of the two estimates the \ac{DO} change at each time step from advection, $DO_{adv}$. In practice, the simulated tidal signal was used to estimate $DO_{adv}$:
\begin{equation} \label{do_advp}
DO_{adv} \propto H
\end{equation}
\begin{equation} \label{do_adv}
DO_{adv} = 2\cdot a + a \cdot \frac{H- \min H}{\max H - \min H}
\end{equation}
where $a$ is analogous to $k$ in \cref{deltx} and is chosen as the transformation parameter to standardize change in \ac{DO} from tidal height change to desired units.  For example, $a = 1$ will convert $H$ to a scale that simulates changes in \ac{DO} from tidal advection that range from +/- 1 mg L$^{-1}$.  The final time series for observed \ac{DO} was the sum of biological \ac{DO} and advection \ac{DO} (\cref{do_obs,fig:do_sim}).

@@

Multiple time series were simulated by varying the conditions in \cref{do_obs,do_bio,do_unc,do_obs_all,do_sin,do_unc_n,deltdo,deltx,do_advp,do_adv}. Specifically, the simulated data varied in the relative amount of noise in the measurement ($e_{pro}$, $e_{obs}$), relative amplitude of the diel \ac{DO} component ($DO_{die}$), and degree of association of the tide with the \ac{DO} signal ($DO_{adv}$).  Three levels were evaluated for each variable: relative noise as 0, 1, and 2 standard deviations for both process and observation uncertainty, amplitude of diel biological \ac{DO} as 0, 1, and 2 mg L$^{-1}$, and \ac{DO} change from tidal advection as 0, 1, and 2 mg L$^{-1}$. A total of 81 time series were created based on the unique combinations of parameters (\cref{fig:sim_ex}).  Half-window widhts (day, hour of day, and tide height) were evaluated for each simulation: decimal time as 1, 3, and 6 days, time of day as 1, 3, and 6 hours, and tidal height as 0.25, 0.5, and 1 as a proportion of the total range given the height at the center of the window.  The window widths were chosen based on preliminary assessments that suggested a large range in model performance was described by these values.  In total, 27 window width combinations were evaluated for each of 81 simulated time series, producing results for 2187 weighted regressions.

The filtered \ac{DO} time series were compared to the simulated data to evaluate the ability of weighted regression to characterize the biological \ac{DO} time series in \cref{do_obs}. Results were summarized using Pearson correlation coefficients and the \ac{RMSE} between the filtered time series and the biological \ac{DO} time series as a known component of the observed.  Overall, the weighted regressions produced filtered time series that were similar to the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2}, results for each simulation can be viewed using the link in the \hyperref[multi]{multimedia} section).  The median correlation for all time series and window widths between the filtered and biological values was \Sexpr{form_fun(perf_medians['cor'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'cor'])} to \Sexpr{form_fun(perf_rngs[2, 'cor'])}.  Mean error was \Sexpr{form_fun(perf_medians['err'])}, with values ranging from \Sexpr{form_fun(perf_rngs[1,'err'], 0, 0, 0)} to \Sexpr{form_fun(perf_rngs[2, 'err'])}.  Simulations with very poor performance (e.g., negative correlations) were those that had minimum widths for day windows and maximum widths for hour windows, or were those with the \ac{DO} signal composed entirely of noise from observation uncertainty. As expected, simulations with no biological or tidal influence had filtered time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero).

Characteristics of \ac{DO} time series that contributed to improved model performance were increasing amplitude of the diel \ac{DO} component ($DO_{die}$) and increasing process error ($e_{pro}$), whereas increasing observation error contributed to decreased performance (\cref{tab:dtd_perf1,fig:err_surf1}).  Model performance decreased slightly with increasing tidal effects (i.e., increasing magnitude of $DO_{adv}$).  Increasing widths for day and tidal height windows contributed to improved model performance, whereas reduced performance was observed with increasing hour windows (\cref{tab:dtd_perf2,fig:err_surf2}).  Graphical summaries of model performance by simulation parameters (\cref{fig:err_surf1}) and half window widths (\cref{fig:err_surf2}) support the general trends described by \cref{tab:dtd_perf1,tab:dtd_perf2}.

### 2014-09-24 swmp_noise.Rnw
changed means to medians

\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
% \usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

%%%%%%
% refs
\begin{singlespace}
\bibliographystyle{M:/docs/bibtex_bst/apalike_mine}
\bibliography{M:/docs/ref_diss}
\end{singlespace}
\clearpage

@@

# calculate mean, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[2:8], # note indexing
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          min(y$cor),
          quantile(y$cor, 0.25),
          mean(y$cor),
          quantile(y$cor, 0.75),
          max(y$cor),
          min(y$err),
          quantile(y$err, 0.25),
          mean(y$err),
          quantile(y$err, 0.75),
          max(y$err)
        )
    })}
  )

# rename first column for combining, create column for parameter,  then combine
dtd_perf <- lapply(dtd_perf, 
  function(x) { 
    Parameter <- names(x)[1]
    names(x)[1] <- 'Level'
    x[,1] <- factor(x[,1])
    Parameter <- rep(Parameter, nrow(x))
    x <- data.frame(Parameter, x)
    x
    }
  )
dtd_perf <- do.call('rbind', dtd_perf)
names(dtd_perf) <- c('Parameter', 'Level', 'Min cor', 'Low cor', 'Mean cor', 'High cor', 'Max cor', 'Min err', 'Low err', 'Mean err', 'High err', 'Max err')

@@

# names for row categories in table
Parms <- c('$\\boldsymbol{DO_{die}}$', 
  '$\\boldsymbol{DO_{adv}}$',  
  '$\\boldsymbol{\\epsilon_{pro}}$', 
  '$\\boldsymbol{\\epsilon_{obs}}$'
  )
tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary (range, mean, percentiles) of correlations and error estimates comparing detided and biological \\ac{DO} time series for different simulation parameters ($DO_{die}$, $DO_{adv}$, $\\epsilon_{pro}$, $\\epsilon_{obs}$).  Values represent averages from multiple simulations with common parameters (e.g., row one is a summary of all simulations for which diel \\ac{DO} component was zero).'

@@

latex( 
  tab,
  file = '',
  where = 'h',
  rowlabel = 'Parameter',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 4),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}', 'Mean', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf1'
  )
@

@@

# calculate mean, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[1:8],
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          min(y$cor),
          quantile(y$cor, 0.25),
          mean(y$cor),
          quantile(y$cor, 0.75),
          max(y$cor),
          min(y$err),
          quantile(y$err, 0.25),
          mean(y$err),
          quantile(y$err, 0.75),
          max(y$err)
        )
    })}
  )

# rename first column for combining, create column for parameter,  then combine
dtd_perf <- lapply(dtd_perf, 
  function(x) { 
    Parameter <- names(x)[1]
    names(x)[1] <- 'Level'
    x[,1] <- factor(x[,1])
    Parameter <- rep(Parameter, nrow(x))
    x <- data.frame(Parameter, x)
    x
    }
  )
dtd_perf <- do.call('rbind', dtd_perf)
names(dtd_perf) <- c('Parameter', 'Level', 'Min cor', 'Low cor', 'Mean cor', 'High cor', 'Max cor', 'Min err', 'Low err', 'Mean err', 'High err', 'Max err')

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary (range, mean, percentiles) of correlations and error estimates comparing detided and biological \\ac{DO} time series for simulations using different half window widths in the weighted regressions (days, hours, and proportion of tidal range).  Values represent averages from multiple simulations with common window values (e.g., row one is a summary of all simulations for which the half window width was one day).'

@@

latex( 
  tab,
  file = '',
  rowlabel = 'Window',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 3),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}',  'Mean', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf2'
  )
@

>>>>

\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

%%%%%%
% refs
\begin{singlespace}
\bibliographystyle{apalike_mine}
\bibliography{ref_diss}
\end{singlespace}
\clearpage

@@

# calculate mean, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[2:8], # note indexing
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          min(y$cor),
          quantile(y$cor, 0.25),
          median(y$cor),
          quantile(y$cor, 0.75),
          max(y$cor),
          min(y$err),
          quantile(y$err, 0.25),
          median(y$err),
          quantile(y$err, 0.75),
          max(y$err)
        )
    })}
  )

# rename first column for combining, create column for parameter,  then combine
dtd_perf <- lapply(dtd_perf, 
  function(x) { 
    Parameter <- names(x)[1]
    names(x)[1] <- 'Level'
    x[,1] <- factor(x[,1])
    Parameter <- rep(Parameter, nrow(x))
    x <- data.frame(Parameter, x)
    x
    }
  )
dtd_perf <- do.call('rbind', dtd_perf)
names(dtd_perf) <- c('Parameter', 'Level', 'Min cor', 'Low cor', 'Median cor', 'High cor', 'Max cor', 'Min err', 'Low err', 'Median err', 'High err', 'Max err')

@@

# names for row categories in table
Parms <- c('$\\boldsymbol{DO_{die}}$', 
  '$\\boldsymbol{DO_{adv}}$',  
  '$\\boldsymbol{\\epsilon_{pro}}$', 
  '$\\boldsymbol{\\epsilon_{obs}}$'
  )
tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary (range, median, percentiles) of correlations and error estimates comparing detided and biological \\ac{DO} time series for different simulation parameters ($DO_{die}$, $DO_{adv}$, $\\epsilon_{pro}$, $\\epsilon_{obs}$).  Values represent averages from multiple simulations with common parameters (e.g., row one is a summary of all simulations for which diel \\ac{DO} component was zero).'

@@

latex( 
  tab,
  file = '',
  where = 'h',
  rowlabel = 'Parameter',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 4),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}', 'Median', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf1'
  )
@

@@

# calculate median, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[1:8],
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          min(y$cor),
          quantile(y$cor, 0.25),
          median(y$cor),
          quantile(y$cor, 0.75),
          max(y$cor),
          min(y$err),
          quantile(y$err, 0.25),
          median(y$err),
          quantile(y$err, 0.75),
          max(y$err)
        )
    })}
  )

# rename first column for combining, create column for parameter,  then combine
dtd_perf <- lapply(dtd_perf, 
  function(x) { 
    Parameter <- names(x)[1]
    names(x)[1] <- 'Level'
    x[,1] <- factor(x[,1])
    Parameter <- rep(Parameter, nrow(x))
    x <- data.frame(Parameter, x)
    x
    }
  )
dtd_perf <- do.call('rbind', dtd_perf)
names(dtd_perf) <- c('Parameter', 'Level', 'Min cor', 'Low cor', 'Median cor', 'High cor', 'Max cor', 'Min err', 'Low err', 'Median err', 'High err', 'Max err')

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary (range, median, percentiles) of correlations and error estimates comparing detided and biological \\ac{DO} time series for simulations using different half window widths in the weighted regressions (days, hours, and proportion of tidal range).  Values represent averages from multiple simulations with common window values (e.g., row one is a summary of all simulations for which the half window width was one day).'

@@

latex( 
  tab,
  file = '',
  rowlabel = 'Window',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 3),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}',  'Median', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf2'
  )
@
